---
title: "API in R"
output: html_notebook
---
This is the first exercise with API using R. It has been done using Paul Bradshaw's tutorial. 

# Store the URL
First, I get the url from the website and I store it as an object
```{r}
url <- "http://api.postcodes.io/postcodes/b422su"
```
R asks me to install curl package when running JSON function

```{r}
install.packages('curl')
```
Now run JSON function with the url and the object appear as data in my environment. 

```{r}
jsoneg <- fromJSON(url)
```

```{r}
jsoneg
```
# Accessing to one item
```{r}
jsoneg[["status"]]
```

```{r}
jsoneg[['result']][['codes']][['ccg']]
```

# Loop
To use more postcodes I need to create a loop. First, I make a vector with the postcodes I want to use.
```{r}
postcodes <- c("B422SU","BL23QQ","B735XJ", "B168JT")
```

Then, the "for" which is the function for the "loop". That means "for each item stores in the object postcodes pick the value i and print to me"
```{r}
for (i in postcodes) { 
  print(i)
}
```
And adding more details to what we want the function does for us. 
```{r}
for (i in postcodes){
  print(paste("http://api.postcodes.io/postcodes/",i, sep=""))
}
```
# Making more complex

For each item stored in postcodes, pick the url, build one like I point and store it in the object called url. Then, grab this object, run the function fromJSON and store it as jsoneg. And finally, print the details I selected. 
```{r}
for (i in postcodes){
  url <- paste("http://api.postcodes.io/postcodes/",i, sep="")
  jsoneg <- fromJSON(url)
  #drill down into one branch and print the value
  print(jsoneg[['result']][['parliamentary_constituency']])
}
```
# Store the results

```{r}
#This creates an empty list called 'resultslist'
resultslist = c()
for (i in postcodes){
  url <- paste("http://api.postcodes.io/postcodes/",i, sep="")
  jsoneg <- fromJSON(url)
  print(jsoneg[['result']][['parliamentary_constituency']])
  #This time we store the results of drilling down into part of the JSON
  constituency <- jsoneg[['result']][['parliamentary_constituency']]
  #Then we add it to the list
  resultslist = c(resultslist, constituency)
}
```

I want another element to my list in another column

```{r}
resultslist2 = c()
for (i in postcodes) {
  url <- paste("http://api.postcodes.io/postcodes/",i, sep="")
  jsoneg <- fromJSON(url)
  print(jsoneg[['result']][['parliamentary_constituency']])
  constituency <- jsoneg[['result']][['parliamentary_constituency']]
  print(jsoneg[["result"]][["ccg"]])
  ccg <- jsoneg[["result"]][["ccg"]]
  resultslist = c(resultslist, constituency)
  resultslist2 = c(resultslist2, ccg)
}
```

A table with both lists?

```{r}
data.frame(resultslist, resultslist2)
```

Changing the names. First, store like an Data object
```{r}
table <- data.frame(resultslist, resultslist2)
```
Now, change them
```{r}
names(table) <- c("Primera", "Segunda")
View(table)
```

And store the function

```{r}
formurls <- function (postcodes) {
  for (i in postcodes) {
    url <- paste("http://api.postcodes.io/postcodes/",i, sep="")
  jsoneg <- fromJSON(url)
  print(jsoneg[['result']][['parliamentary_constituency']])
  constituency <- jsoneg[['result']][['parliamentary_constituency']]
  print(jsoneg[["result"]][["ccg"]])
  ccg <- jsoneg[["result"]][["ccg"]]
  resultslist = c(resultslist, constituency)
  resultslist2 = c(resultslist2, ccg)
    }
  }
```
Checking the function. First creating a new vector.
```{r}
Vicpost <- c("B168JT", "B83QU", "B65JT")
```
Using our function
```{r}
formurls(Vicpost)
View(resultslist)

```

